Analysis, Prototyping and Locomotion Control of a Quadruped Robot\\

### 2023-08-31 LARS_paper/paper.tex
Update Table2 and Table3 positions
Update author informations

%TODO
\author{\IEEEauthorblockN{1\textsuperscript{st} Lucas Souza}
  \IEEEauthorblockA{\textit{Departament of Robotics} \\
    \textit{SENAI CIMATEC}\\
    Salvador, Brazil \\
    lucaslinssouza@gmail.com}
  \and
  \IEEEauthorblockN{2\textsuperscript{nd} Felipe Mohr}
  \IEEEauthorblockA{\textit{Departament of Robotics} \\
    \textit{SENAI CIMATEC}\\
    Salvador, Brazil \\
    felipe18mohr@gmail.com}
  \and
  \IEEEauthorblockN{3\textsuperscript{rd} Brenda Alencar}
  \IEEEauthorblockA{\textit{Departament of Robotics} \\
    \textit{SENAI CIMATEC}\\
     Salvador, Brazil \\
    brenda.s1602@outlook.com}
}

@@

\begin{table}[b]
  \centering
  \caption{Velocity and stability results.}
  \scalebox{1.3}{
  \begin{tabular}{ccccc}
    \hline
    \textbf{Test}              & \textbf{1}   & \textbf{2}  & \textbf{3}   & \textbf{4}   \\ \hline
    Ter.                       & Flat         & Flat        & Uneven       & Uneven       \\ \hline
    \begin{tabular}[c]{@{}c@{}}S. C. \end{tabular} & No           & Yes         & No           & Yes          \\ \hline
    \begin{tabular}[c]{@{}c@{}}Vel. \\ $(cm/s)$ \end{tabular} & 2.15         & 3.68        & 2.03         & 2.39         \\ \hline
    \begin{tabular}[c]{@{}c@{}} $\sigma_{Vel}$  \\ $(cm/s)$ \end{tabular} & 0.040        & 0.075       & 0.016        & 0.047        \\ \hline
    \begin{tabular}[c]{@{}c@{}} $\Delta_{Roll}$ \end{tabular} & 12.59\degree & 8.81\degree & 13.37\degree & 11.13\degree \\\hline
    \begin{tabular}[c]{@{}c@{}} $\sigma_{Roll}$ \end{tabular} & 2.54\degree  & 2.36\degree & 0.78\degree  & 1.47\degree  \\ \hline
    \begin{tabular}[c]{@{}c@{}} $\Delta_{Pitch}$ \end{tabular} & 11.55\degree & 8.31\degree & 15.19\degree & 12.09\degree \\ \hline
    \begin{tabular}[c]{@{}c@{}} $\sigma_{Pitch}$ \end{tabular} & 1.89\degree  & 2.63\degree & 1.44\degree  & 1.66\degree  \\ \hline
  \end{tabular}
  }
  \label{tab:vel_stab}
  % \vspace{-\baselineskip}
\end{table}

@@

\begin{table}[tb]
  \centering
  \caption{Angular velocity and stability results.}
  \scalebox{1.3}{
  \begin{tabular}{ccc}
    \hline
    \textbf{Test}              & \textbf{1}   & \textbf{2}   \\ \hline
    Ter.                       & Uneven       & Uneven       \\ \hline
    \begin{tabular}[c]{@{}c@{}}S. C. \end{tabular} & No           & Yes          \\ \hline
    \begin{tabular}[c]{@{}c@{}}Angular vel. \\ $(rad/s)$ \end{tabular} & 0.19         & 0.19         \\ \hline
    \begin{tabular}[c]{@{}c@{}} $\sigma_{Ang. Vel.}$  \\ $(rad/s)$ \end{tabular} & 0.006        & 0.007        \\ \hline
    \begin{tabular}[c]{@{}c@{}} $\Delta_{Roll}$ \end{tabular} & 16.16\degree & 16.84\degree \\\hline
    \begin{tabular}[c]{@{}c@{}} $\sigma_{Roll}$ \end{tabular} & 1.88\degree  & 2.6\degree  \\ \hline
    \begin{tabular}[c]{@{}c@{}} $\Delta_{Pitch}$ \end{tabular} & 11.79\degree & 12.89\degree \\ \hline
    \begin{tabular}[c]{@{}c@{}} $\sigma_{Pitch}$ \end{tabular} & 1.05\degree  & 1.41\degree  \\ \hline
  \end{tabular}
  }
  \label{tab:ang_vel_stab}
  % \vspace{-\baselineskip}
\end{table}

>>>>

%TODO
\author{\IEEEauthorblockN{1\textsuperscript{st} Lucas Souza}
  \IEEEauthorblockA{\textit{Autonomous Robotics Research Center} \\
    \textit{Technology Innovation Institute}\\
    Abu Dhabi, UAE  \\
    lucas.souza@tii.ae}
  \and
  \IEEEauthorblockN{2\textsuperscript{nd} Felipe Mohr}
  \IEEEauthorblockA{\textit{Robotics Departament} \\
    \textit{SENAI CIMATEC}\\
    Salvador, Brazil \\
    felipe.barreto@fieb.org.br}
  \and
  \IEEEauthorblockN{3\textsuperscript{rd} Brenda Alencar}
  \IEEEauthorblockA{\textit{Robotics Departament} \\
    \textit{SENAI CIMATEC}\\
    Salvador, Brazil \\
    brenda.alencar@fieb.org.br}
}

@@

\begin{table}[!h]
  \centering
  \caption{Velocity and stability results.}
  \scalebox{1.3}{
  \begin{tabular}{ccccc}
    \hline
    \textbf{Test}              & \textbf{1}   & \textbf{2}  & \textbf{3}   & \textbf{4}   \\ \hline
    Ter.                       & Flat         & Flat        & Uneven       & Uneven       \\ \hline
    \begin{tabular}[c]{@{}c@{}}S. C. \end{tabular} & No           & Yes         & No           & Yes          \\ \hline
    \begin{tabular}[c]{@{}c@{}}Vel. \\ $(cm/s)$ \end{tabular} & 2.15         & 3.68        & 2.03         & 2.39         \\ \hline
    \begin{tabular}[c]{@{}c@{}} $\sigma_{Vel}$  \\ $(cm/s)$ \end{tabular} & 0.040        & 0.075       & 0.016        & 0.047        \\ \hline
    \begin{tabular}[c]{@{}c@{}} $\Delta_{Roll}$ \end{tabular} & 12.59\degree & 8.81\degree & 13.37\degree & 11.13\degree \\\hline
    \begin{tabular}[c]{@{}c@{}} $\sigma_{Roll}$ \end{tabular} & 2.54\degree  & 2.36\degree & 0.78\degree  & 1.47\degree  \\ \hline
    \begin{tabular}[c]{@{}c@{}} $\Delta_{Pitch}$ \end{tabular} & 11.55\degree & 8.31\degree & 15.19\degree & 12.09\degree \\ \hline
    \begin{tabular}[c]{@{}c@{}} $\sigma_{Pitch}$ \end{tabular} & 1.89\degree  & 2.63\degree & 1.44\degree  & 1.66\degree  \\ \hline
  \end{tabular}
  }
  \label{tab:vel_stab}
  % \vspace{-\baselineskip}
\end{table}

@@

\begin{table}[!h]
  \centering
  \caption{Angular velocity and stability results.}
  \scalebox{1.3}{
  \begin{tabular}{ccc}
    \hline
    \textbf{Test}              & \textbf{1}   & \textbf{2}   \\ \hline
    Ter.                       & Uneven       & Uneven       \\ \hline
    \begin{tabular}[c]{@{}c@{}}S. C. \end{tabular} & No           & Yes          \\ \hline
    \begin{tabular}[c]{@{}c@{}}Angular vel. \\ $(rad/s)$ \end{tabular} & 0.19         & 0.19         \\ \hline
    \begin{tabular}[c]{@{}c@{}} $\sigma_{Ang. Vel.}$  \\ $(rad/s)$ \end{tabular} & 0.006        & 0.007        \\ \hline
    \begin{tabular}[c]{@{}c@{}} $\Delta_{Roll}$ \end{tabular} & 16.16\degree & 16.84\degree \\\hline
    \begin{tabular}[c]{@{}c@{}} $\sigma_{Roll}$ \end{tabular} & 1.88\degree  & 2.6\degree  \\ \hline
    \begin{tabular}[c]{@{}c@{}} $\Delta_{Pitch}$ \end{tabular} & 11.79\degree & 12.89\degree \\ \hline
    \begin{tabular}[c]{@{}c@{}} $\sigma_{Pitch}$ \end{tabular} & 1.05\degree  & 1.41\degree  \\ \hline
  \end{tabular}
  }
  \label{tab:ang_vel_stab}
  % \vspace{-\baselineskip}
\end{table}
